---
title: "Starter Survey 2017"
author: "Hugo SECHIER"
date: "November 3, 2017"
output: 
  html_notebook: 
    code_folding: show
    highlight: haddock
    theme: readable
---


# Introduction

This is an analysis of the responses to Kaggle's 2017 user survey. In total, 16,716 people responded to enough of the survey to be analyzed. 
Allow to this survey and this following analysis, we can know how to manage and launch a data science team. 

## Data Source

All data was collected by [Kaggle](https://www.kaggle.com) in their 2017 user survey. The survey was available to users from August 7 - August 25, 2017. 

Inspired by [this kernel](https://www.kaggle.com/amberthomas/kaggle-2017-survey-results)

## Installing Necessary Packages

```{r}
# For Data Cleaning
library(tidyverse)

library(ggplot2)
library(plotly)
library(alluvial)
# For text analysis and word clouds
library(tm)
library(SnowballC)
library(wordcloud)
```

## Loading Data

Based on the way this data is structured, I want to keep the first row as column headers. 

```{r}
# Import multiple choice data
Survey <- read.csv('../input/multipleChoiceResponses.csv', stringsAsFactors = TRUE, header = TRUE)

# Import freeform responses
rawFFData <- read.csv('../input/freeformResponses.csv', stringsAsFactors = FALSE, header = TRUE)

# Import the actual questions asked
schema <- read.csv('../input/schema.csv', stringsAsFactors = FALSE, header = TRUE)
```

Last, I need to import the currency conversion rates for use later. 
```{r}
conversionRates <- read.csv('../input/conversionRates.csv', header = TRUE)
```
## Basic clean data 
### Id 
We're creating an id column. It will use later 
```{r}
Survey = Survey %>% 
  mutate(id = 1:nrow(Survey))
```

### Age 
We have to cut the age in order to analyse easiest possible. 

```{r}
Survey$Age <- as.numeric(as.character(Survey$Age))
ggplot(Survey,aes(Age)) +
  geom_histogram(bins = 100,color = "blue")
```
```{r}
breaks_Age = c(min(Survey$Age,na.rm = T),"20","25","30","45",max(Survey$Age,na.rm = T))
Survey$Age = cut(Survey$Age,breaks_Age,include.lowest = TRUE)
```





## What kind of company works ? 
size

## Where launch your futur company ? 
map

## What kind of equipment use ? 
computer
## Where can you find data scientist ? 
School 
Reconversion 

```{r}
df = Survey %>% 
  select(CurrentJobTitleSelect) %>% 
  group_by(CurrentJobTitleSelect) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  filter(CurrentJobTitleSelect != "")
  
custom_text = sprintf("Job: %s <b> freq : %d",df$CurrentJobTitleSelect,df$count)
p = ggplot(df,aes(x = reorder(CurrentJobTitleSelect,-count),y = count,fill = reorder(CurrentJobTitleSelect,-count),text = custom_text))+
  geom_bar(stat = "identity")
ggplotly(p,tooltip = "text")
```


```{r}
foo = Survey %>% 
  select(Age,CurrentJobTitleSelect,DataScienceIdentitySelect) %>% 
  filter(CurrentJobTitleSelect != "") %>% 
  filter(DataScienceIdentitySelect != "") %>% 
  filter(CurrentJobTitleSelect %in% df$CurrentJobTitleSelect[1:10]) %>% 
  ungroup() %>% 
  filter(complete.cases(.)) %>% 
  group_by(Age,CurrentJobTitleSelect,DataScienceIdentitySelect) %>% 
  summarise(count = n()) %>% 
  droplevels()

alluvial(foo[,1:3], freq=foo$count,
         col = ifelse(foo$DataScienceIdentitySelect == "Yes", "orange", "grey"),
         border = ifelse(foo$DataScienceIdentitySelect == "Yes", "orange", "grey"),
         cex = 0.7
)

```


```{r}
DS = Survey$id[which(Survey$DataScienceIdentitySelect == "Yes")]
DS = c(DS,Survey$id[which(Survey$CurrentJobTitleSelect == "Data Scientist")])
foo = Survey %>% 
  mutate(IsDS = id %in% DS) %>% 
  select(FormalEducation,MajorSelect,CurrentJobTitleSelect,IsDS) %>% 
  filter(CurrentJobTitleSelect != "") %>% 
  filter(FormalEducation != "") %>% 
  filter(MajorSelect != "") %>% 
  #filter(CurrentJobTitleSelect %in% df$CurrentJobTitleSelect[1:10]) %>% 
  ungroup() %>% 
  filter(complete.cases(.)) %>% 
  group_by(FormalEducation,MajorSelect,CurrentJobTitleSelect,IsDS) %>% 
  summarise(count = n()) %>% 
  filter(count > 50) %>% 
  droplevels()

alluvial(foo[,1:4], freq=foo$count,
         col = ifelse(foo$IsDS == "FALSE", "orange", "grey"),
         border = ifelse(foo$IsDS == "FALSE", "orange", "grey"),
         #hide = foo$count < 50,
         cex = 0.7
)

```
This graph can help you to know where you can find DS. 
For example : 
- Most of the bachelor's degree are not DS
- A good Software Developer with a Doctoral degree can be as DS. Otherwise, it's not a DS.  

## How can you form your data scientist ? 

## Which data scientist are happy ? 

## Which salary give on your data scientist ?
predict the salary (model regression)



